Life in the canopy: Community trait assessments reveal substantial functional diversity among fern epiphytes

### 2020-02-19 ms/SI.rmd
Make correlation plot in plan

# Load analysis results
loadd(list = c(
  "taxonomic_data_for_si",
  "trait_data_for_si",
  "climate_ancova_results",
  "phylosig_binary_traits_strict",
  "correlated_evo_test_strict",
  "best_fit_div_models_moran",
  "func_comm_struc_combined",
  "climate_model_summaries",
  "climate_models",
  "div_el_models",
  "div_el_model_summaries",
  "div_el_model_parameter_summaries",
  "cwsd_scatterplot"), 
  cache = canopy_cache)

@@

```{r Fig-S2, fig.height = 8, fig.width = 4, fig.cap = ""}

# Tweak names for easier viewing
func_comm_struc_combined_renamed <-
func_comm_struc_combined %>%
  mutate(dataset = str_remove_all(dataset, "func_comm_struc_test_fern_traits_")) %>%
  mutate(dataset = str_remove_all(dataset, "\\.pool")) %>%
  mutate(dataset = str_replace_all(dataset, "all_reduced", "reduced")) %>%
  mutate(dataset = str_remove_all(dataset, "scaled_")) %>%
  mutate(dataset = str_replace_all(dataset, "log_", "log-trans_"))

# Don't need log-transformed sets that don't include log-transformed traits
func_comm_struc_combined_renamed <- 
  func_comm_struc_combined_renamed %>%
  filter(
    !dataset %in% c("log-trans_gameto", "log-trans_other")
  )

# Convert to wide format, run corrr: MPD
mpd_corr <-
  func_comm_struc_combined_renamed %>%
  select(dataset, site, habit, mpd.obs.z) %>%
  spread(dataset, mpd.obs.z) %>%
  select(-site, -habit) %>%
  correlate %>% 
  rearrange(absolute = FALSE) # arrange so most correlated variables are closest

# Make plot 
# Modified from https://github.com/tidymodels/corrr/issues/35
order <- mpd_corr %>% 
  select(-rowname) %>% 
  colnames()

mpd_corr_plot <-
mpd_corr %>% 
  stretch(na.rm = TRUE) %>%
  mutate_at(c("x", "y"), forcats::fct_relevel, ... = order) %>% 
  ggplot(aes(x, y, fill = r)) +
  geom_tile() +
  geom_text(aes(label = as.character(fashion(r))), color = "white", size = 3) +
  scale_fill_scico(palette = "roma", breaks = c(-1, 1)) +
  labs(x = NULL, y = NULL, subtitle = "(a)") +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    plot.subtitle = element_text(face = "bold"),
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)
  )

# Convert to wide format, run corrr: MNTD
mntd_corr <-
  func_comm_struc_combined_renamed %>%
  select(dataset, site, habit, mntd.obs.z) %>%
  spread(dataset, mntd.obs.z) %>%
  select(-site, -habit) %>%
  correlate %>% 
  rearrange(absolute = FALSE)

mntd_corr_plot <-
  mntd_corr %>% 
  stretch(na.rm = TRUE) %>%
  mutate_at(c("x", "y"), forcats::fct_relevel, ... = order) %>% # Use same order as MPD
  ggplot(aes(x, y, fill = r)) +
  geom_tile() +
  geom_text(aes(label = as.character(fashion(r))), color = "white", size = 3) +
  scale_fill_scico(palette = "roma", breaks = c(-1, 1)) +
  labs(x = NULL, y = NULL, subtitle = "(b)") +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    plot.subtitle = element_text(face = "bold"),
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)
  )

fig_s2 <- mpd_corr_plot + mntd_corr_plot + plot_layout(nrow = 2, ncol = 1)

fig_s2 <- fig_s2 + plot_annotation(theme = theme(plot.margin = margin(
      0.2, 0.2, 0.2, 0.2, unit = "in")))

fig_s2
```

>>>>

# Load analysis results
loadd(list = c(
  "taxonomic_data_for_si",
  "trait_data_for_si",
  "climate_ancova_results",
  "phylosig_binary_traits_strict",
  "correlated_evo_test_strict",
  "best_fit_div_models_moran",
  "func_div_corr_plot",
  "climate_model_summaries",
  "climate_models",
  "div_el_models",
  "div_el_model_summaries",
  "div_el_model_parameter_summaries",
  "cwsd_scatterplot"), 
  cache = canopy_cache)

@@

```{r Fig-S2, fig.height = 8, fig.width = 4, fig.cap = ""}
func_div_corr_plot
```
